Landform boundary effects on Holocene forager landscape use in arid South Australia

### 2017-02-01 analysis/paper/paper.Rmd
update acknowledgements

This work was undertaken under a contract with BHP Billiton that includes research support. Other financial support for Ben Marwick came from a Luce/ACLS Post-doctoral fellowship (B9471 01 180401 7301), a grant from the Herbert H. Gowen International Studies Endowment (UW Office of Global Affairs), and an Australian Research Council Future Fellowship (FT140100101).

>>>>

The fieldwork component of this study was undertaken in accordance with the Olympic Dam Agreement between BHP Billiton and the Aboriginal native title claimant groups under a contract with BHP Billiton that included research support. Other financial support for Ben Marwick came from a Luce/ACLS Post-doctoral fellowship (B9471 01 180401 7301), a grant from the Herbert H. Gowen International Studies Endowment (UW Office of Global Affairs), and an Australian Research Council Future Fellowship (FT140100101).
